MA_Results

### 2022-05-29 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
table 1 rough draft done

```{r child="MS_Tables.Rmd", echo=FALSE}
```
```{r child="MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->

@@

Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for. A special type of function called a method can only be applied to a pre-defined data structure. Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022]. For example, when generalising a model developed for the Australian context to a UK context, one could create a class (data structure) that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.

@@

- **E1: Model code is distributed as libraries of functions**  <!-- Modified (lost ref to OOP and merged with M2) -->

@@

### Licensed Models
```{r}
# Adapted fom: https://seankross.com/2016/08/02/How-R-Packages-are-Licensed.html
sorting_hat <- function(student, houses){
  choice <- purrr::map_lgl(houses, grepl, x = student)
  if(!any(choice)){
    return("Other")
  } else {
    return((houses[choice])[1])
  }
}
license_table <- table(utils::available.packages()[,"License"])
names(license_table) %<>%
  purrr::map_chr(function(x){
    sorting_hat(x, c("Apache", "Artistic", "CC", "BSD", "MIT", "GPL"))
  })  
license_tbl <- as.data.frame(license_table) %>%
  dplyr::rename(License = Var1) %>%
  dplyr::group_by(License) %>%
  dplyr::summarize(Freq = sum(Freq)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(dplyr::desc(Freq))
licenses <- license_tbl$Freq
gpl_pc_dbl<- round(license_tbl$Freq[license_tbl$License=="GPL"]/sum(license_tbl$Freq)*100,2) 
```

@@

- **Y2: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
- **Y2: Non-technical users can configure and run models via simple user-interfaces** <!-- Was Y1 -->

@@

### Software
We have written six R packages to support the development and curation of model code and data. The purpose of each package, the TIMELY standards they support and the existing R packages they depend on are summarised in Table 1.

```{r cpkgs, tab.cap='Software', tab.id = 'cpkgs', echo = F, results = 'asis'}
      tb <- tibble::tibble(Package = c("ready4","ready4fun"),
                                                    Version = Package %>%
                        purrr::map_chr(~utils::packageDescription(.x) %>%
                                         purrr::pluck("Version")),
                           Depends = Package %>%
                         purrr::map(~ {
                           utils::packageDescription(.x) %>%
                             `[`(c("Depends", "Imports")) %>%
                             purrr::map(~{
                               if(is.null(.x)){
                                 character(0)
                               }else{
                                 .x %>%
                                   strsplit(",\\n") %>%
                                   purrr::flatten_chr() %>%
                                   purrr::map(~strsplit(.x,", ") %>%
                                                purrr::flatten_chr()) %>%
                                   purrr::flatten_chr() %>% sort() %>%
                                   purrr::discard(~startsWith(.x,"R "))
                               }
                             }) %>%
                             purrr::flatten_chr() %>%
                             unique() %>%
                             sort() %>%
                         purrr::map_chr(~{
                           updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                           problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                             unname()
                           if(!is.na(problem_idx_1L_chr))
                             updated_1L_chr <- updated_1L_chr %>%
                             stringr::str_sub(end = problem_idx_1L_chr-1)
                           updated_1L_chr %>% trimws(which = "left")
                         })
                         })

                       ) 
# packages_df <- data.frame(Name = c("ready4", "ready4fun"),
#                           Purpose = c("Provide framework modules and syntax",
#                                       "Standardise and partially automate the authoring and documenting of functions."),
#                           `Supports standard` = c("AAAA","BBB"),
#                           Depends = c("A","B")) 
params_ls<-list(output_type_1L_chr="PDF")
tb  %>%
    ready4show::print_table(output_type_1L_chr = params_ls$output_type_1L_chr,
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params_ls$output_type_1L_chr=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL)
```

>>>>

```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->

@@

Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for. A special type of function called a method can only be applied to a pre-defined class of data structure. Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022]. For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.

@@

- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->

@@

### Licensed Models
```{r}
# Adapted fom: https://seankross.com/2016/08/02/How-R-Packages-are-Licensed.html
sorting_hat <- function(student, houses){
  choice <- purrr::map_lgl(houses, grepl, x = student)
  if(!any(choice)){
    return("Other")
  } else {
    return((houses[choice])[1])
  }
}
license_table <- table(utils::available.packages()[,"License"])
names(license_table) %<>%
  purrr::map_chr(function(x){
    sorting_hat(x, c("Apache", "Artistic", "CC", "BSD", "MIT", "GPL"))
  })  
license_tbl <- as.data.frame(license_table) %>%
  dplyr::rename(License = Var1) %>%
  dplyr::group_by(License) %>%
  dplyr::summarize(Freq = sum(Freq)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(dplyr::desc(Freq))
#licenses <- license_tbl$Freq
gpl_pc_dbl <- round(license_tbl$Freq[license_tbl$License=="GPL"]/sum(license_tbl$Freq)*100,2) 
```

@@

- **Y1: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
- **Y2: Non-technical users can configure and run models via simple user-interfaces** <!-- Was Y1 -->

@@

```{r, child = child_docs_ls$one, echo=FALSE}
```

### Software
We have written six R packages to support the development and curation of model code and data. The package ready4 defines the framework's syntax and a model module template class. The ready4class package provides tools for creating self-documenting model module classes, while ready4fun is a toolkit for creating the functions (including methods) that are also self-documenting and written in a consistent house style. Model module classes and functions are bundled into R packages with standardised approaches to quality assurance and documentation using the the ready4pack package. Tools for creating and managing model data are included in the ready4use package, while tools for the analysis and reporting of models are included in the ready4show package. The purpose of each package, the TIMELY standards they support and the third party R packages they depend on are summarised in Table 1. <!-- Autogenerate ref -->
